NLTK: A Natural Language Toolkit

### 2002-06-07 technical/handout/handout.tex
- Updated to include new modules; and revised descriptions of some   modules. - Moved URL section to page 1, to make room for more modules.
svn/trunk@713

\documentclass[12pt]{article}
\usepackage{fullpage}

@@

\pagestyle{empty}
\begin{document}
\title{NLTK: A Natural Language Toolkit}
\author{Steven Bird \& Edward Loper}

% clunch:
%\date{Thursday December 12, 2001}

% lsa:
\date{Sunday January 6, 2002}

\maketitle

@@

\section*{Modules}
\thispagestyle{empty}

{\small
\begin{itemize}\nogap

  \item Basics
    \begin{itemize}\nogap
      \item \texttt{token}: Basic classes for processing individual
            elements of text, such as words or sentences. 
      \item \texttt{tree}: Classes for representing tree structures
            over text (such as syntax trees and morphological trees).
      \item \texttt{probability}: Classes that encode frequency
            distributions and probability distributions.
    \end{itemize}

  \item Parsing
    \begin{itemize}\nogap
      \item \texttt{parser}: A standard interface to produce trees
            representing the structure of texts.
      \item \texttt{chartparser}: A flexible parser implementation
            that uses a \emph{chart} to record hypotheses about
            syntactic constituents.
      \item \texttt{srparser\_template}: A partial implementation of a
            shift-reduce parser; completing the implementation was a
            student exercise.
      \item \texttt{chunkparser}: A standard interface for robust
            parsers used to identify non-overlapping linguistic groups
            (such as noun phrases) in unrestricted text.
      \item \texttt{rechunkparser}: A regular-expression based
            implementation of the chunk parser interface.
    \end{itemize}

  \item Text Classification
    \begin{itemize}\nogap
      \item \texttt{classifier}: A standard interface for classifying
          texts into categories.
      \item \texttt{classifier.feature}: A standard way of encoding
          the information used to make classification decisions.
      \item \texttt{classifier.naivebayes}: A text classifier
          implementation based on the Naive Bayes assumption.
      \item \texttt{classifier.maxent}: An implementation of the
          maximum entropy model for text classification; and
          implementations of the GIS and IIS algorithms for training
          the classifier.
      \item \texttt{classifier.featureselection}: A standard interface
          for choosing which features are relevant for making
          classification decisions.
    \end{itemize}

  \item Visualization
    \begin{itemize}\nogap 
      \item \texttt{draw.tree}: A graphical representation for tree
            structures, such as syntax trees and morphological trees. 
      \item \texttt{draw.tree\_edit}: A graphical interface used to
            build and modify tree structures.
      \item \texttt{draw.plot\_graph}: A graphical tool to graph
            arbitrary functions.
      \item \texttt{draw.chart}: An interactive graphical tool used to
            experiment with chart parsers.
    \end{itemize}

\end{itemize}
}
\section*{URL}

@@

>>>>

\documentclass[11pt]{article}
\usepackage{fullpage}

@@

\pagestyle{empty}
\begin{document}
\title{NLTK: A Natural Language Toolkit}
\author{Steven Bird \& Edward Loper}
\date{}

%////////////////////////////////////////
% Page 1: Overview
%////////////////////////////////////////
\maketitle

@@

\section*{URL}

@@

%////////////////////////////////////////
% Page 2: Modules
%////////////////////////////////////////
\section*{Modules}
\thispagestyle{empty}

{%\small
\begin{itemize}\nogap

  \item Basics
    \begin{itemize}\nogap
      \item \texttt{token}: Basic classes for encoding and processing
            individual elements of text, such as words or sentences. 
      \item \texttt{tree}: Classes for representing hierarchical structures
            over text, such as syntax trees.
      \item \texttt{probability}: Classes that encode frequency
            distributions and probability distributions.
    \end{itemize}

  \item Parsing
    \begin{itemize}\nogap
      \item \texttt{cfg}: Basic data types for encoding context free
            grammars. 
      \item \texttt{parser}: A standard interface to produce trees
            representing the structure of texts; and two
            simple implementations of that interface.
      \item \texttt{parser.chart}: A flexible parser implementation
            that uses a \emph{chart} to record hypotheses about
            syntactic constituents. 
      \item \texttt{parser.chunk}: A standard interface for robust
            parsers used to identify non-overlapping linguistic groups
            (such as base noun phrases) in unrestricted text; and a
            regular-expression based implementation of that interface.
      \item \texttt{parser.probabilistic}: A standard interface for
            probabilistic parsers; and two implementations of that
            interface. 
    \end{itemize}

  \item Text Classification
    \begin{itemize}\nogap
      \item \texttt{classifier}: A standard interface for classifying
          texts into categories.
      \item \texttt{classifier.feature}: A standard way of encoding
          the information used to make classification decisions.
      \item \texttt{classifier.naivebayes}: A text classifier
          implementation based on the Naive Bayes assumption.
      \item \texttt{classifier.maxent}: An implementation of the
          maximum entropy model for text classification; and
          implementations of the GIS and IIS algorithms for training
          the classifier.
      \item \texttt{classifier.featureselection}: A standard interface
          for choosing which features are relevant for a given
          classification decision.
    \end{itemize}

  \item Finite State Automata
    \begin{itemize}\nogap 
      \item \texttt{fsa}: Classes for representing finite state
          automata and regular expressions.
    \end{itemize}

  \item Visualization and Interactive Tools
    \begin{itemize}\nogap 
      \item \texttt{draw}: A Tk-based framework for building
            graphical tools.
      \item \texttt{draw.tree}: A graphical representation for
            hierarchical structures.
      \item \texttt{draw.tree\_edit}: A graphical interface used to
            build and modify tree structures.
      \item \texttt{draw.fsa}: A graphical representation for finite
            state automata.
      \item \texttt{draw.plot}: A tool for graphing
            arbitrary functions.
      \item \texttt{draw.chart}: An interactive graphical tool for
            experimenting with the chart parser.
      \item \texttt{draw.rdparser}: An interactive graphical tool for
            exploring the recursive descent parser.
      \item \texttt{draw.srparser}: An interactive graphical tool for
            learning about the shift/reduce parser.
    \end{itemize}

\end{itemize}
}
